\section{User Requirements}
\par The goal of our project is to create two graphical interfaces, the first will control the two transmitter antennas and the second interface to control the two antennas of receiving end.The first interface contains certain information such as the channel on which the data will be transmitted, the frequency of the carrier and the type of the transmitted data (Picture, Sound, Video).

\par \vspace{0.25cm}While the second interface contains information such as the bit error rate (BER) , the received data (Picture, Sound, Video), the Peak Signal to Noise Ratio (PSNR) and the channel of frequency response,
then we will interconnect both interfaces with the transmission code.

\par \vspace{0.25cm}We will also provide the client with source code of our graphical user interface which is to be used with Matlab software. 

\par \vspace{0.25cm}Furthermore, the simulation of the test results that we acquired from the interface of the receiver will be provided.

\par \vspace{0.25cm}But as we begin our project, we realized that we are focusing on the adaptability and optimization of our interfaces, rather than focusing on integrating our interfaces with the transmission code and the devices.

\par \vspace{0.25cm}At the beginning, we proposed the initial design of both interfaces to our client. After we have created the interfaces program, our client demanded to add more parameters. And it turns out that every time we met with our clients, they demanded our program to be more adaptive and more analytical.

\par \vspace{0.25cm}After a few weeks, we began the integration of the transmission code with our interface. We have only able to integrate the SISO method with our program. And the program has limited parameters that we can modify. We have not integrated our program with the devices for the transmission as it's not the objective of our client. With the transmission code, we are able to simulate the process. 

